Predictive Processing Model for an Autonomous Agent

### 2016-12-20 doc/paper.tex
papr onwards

We can take these as these three principles for the design of the
proposed models:

@@

\item Proprioceptive space: any embodied agent has to have a lowest
  level motor system. This is usually represented by a vector of motor
  angles, motor velocities, motor torques, but essentially be any
  given kind of controller. A controller in this sense implies a
  measurement and a prediction defined in the same space. This is the
  point at which we want to engange in interaction with the
  system.

@@

\item Descending propioceptive predictions are equivalent to motor
  commands. Movement quash error at the level of spinal reflexes
  \citep{pickering2014}. Propioceptive predictions elicit motor
  actions, so motor commands, so motor commands are replaced by those
  propioceptive predictions \citep{clark2015}. $S^*_{p(t)}=M_{(t)}$.

@@

Long history, many models: control, development, RL, \ldots{}

\section{Proposed Models}
\label{plan}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Core idea and models}
\label{sec:org733d6e8}
\begin{enumerate}
\item discuss the change of terminology or dichotomies regarding:
\begin{itemize}
\item predictions/motor commands,
\item forward models/inverse models/controllers/policies
\item bottom level black box: different actual forward model (FM)
representations via SOMs, kNN, RLS, GP, \ldots{}
\item see discussion with antonio re: "it's just labels", underneath it is a raw
network of signal flows putting observable quantities into
relation to each other, from which apparent goal-driven behaviour
(teleology) emerges
\end{itemize}
\item two models and their difference in terms of learning dynamics. do
any dynamic properties support or contradict biological motor learning?
\begin{enumerate}
\item M1: explicit goal + error as input
\item M2: error only as input
\item merge with alejandra's two versions (explicit update rule)
\end{enumerate}
\item Experiments
\begin{itemize}
\item deploy models to different robotic systems: Nao, SimpleArm,
Pointmass, two-wheeled
\item timeseries analysis
\item learning transient (arbitrarily fast, see Tin + Poon)
\item explicitly map out the acquired models by sweeping the inputs and
record their outputs
\item what happens under perturbation?
\item long-term adaptation effects: are we only plastic or are we also
stable? do new adaptations overwrite previous ones? does a given
approximator become saturated (just think how critical weight
initialization in neural networks can be) in terms of its adaption
capacity?, can be enforced via decay schedules of learning rate
etc
\end{itemize}
\item discuss, compare with existing approaches like std fwd/inv model
pairs or reinforcement learning
\end{enumerate}

@@

@@

>>>>

We can take these three principles for the design of the proposed models:

@@

\item Discuss the change of terminology or dichotomies regarding:
  \begin{itemize}
  \item predictions/motor commands,
  \item forward models/inverse models/controllers/policies
  \item bottom level black box: different actual forward model (FM)
    representations via SOMs, kNN, RLS, GP, \ldots{}
  \item see discussion with antonio re: "it's just labels", underneath it is a raw
    network of signal flows putting observable quantities into
    relation to each other, from which apparent goal-driven behaviour
    (teleology) emerges
  \end{itemize}

\item Proprioceptive space: any embodied agent has to have a lowest
  level motor system. This is usually represented by a vector of motor
  angles, motor velocities, motor torques, etc but essentially it can be any
  given kind of controller. A controller in this sense implies a
  measurement and a prediction defined in the same space. This is the
  point at which we want to engange in interaction with the
  system.

@@

\item Descending propioceptive predictions are equivalent to motor
  commands. Movement quash error at the level of spinal reflexes
  \citep{pickering2014}. Propioceptive predictions elicit motor
  actions, so motor commands are replaced by those
  propioceptive predictions \citep{clark2015}. $S^*_{p(t)}=M_{(t)}$.

@@

Long history, many models: control, development, RL, neuroscience, ...\ldots{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proposed Models}
\label{plan}

@@

First two basic models and their difference in terms of learning
dynamics. Do any dynamic properties support or contradict biological
motor learning?

\subsection{M1}

The basic building block (BBB) contains an adaptive forward model
(predictor) whose output is the BBB's output. We assume direct
feedback from that module that the output is connected to. The BBB'
inputs are an explicit goal and the prediction error with respect to
the last prediction at ${t-1}$. These inputs taken together encode the
state. Thus the forward model should in principle be able to pick up
on different relations depending on the state. Graphical
representation is given in \autoref{fig:M1}.

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{img/mdl_prediction_error_and_goal.pdf}
  \caption{\label{fig:M1} Basic model M1.}
\end{figure}

\subsection{M2}

This modification of BBB M1 receives only the error as an input. The
model's graph is shown in \autoref{fig:M2}. This model will not be
able to distinguish between situations demanding different
predictions.

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{img/mdl_prediction_error_only.pdf}
  \caption{\label{fig:M2} Basic model M2.}
\end{figure}

\subsection{Extended models connecting modalities}

Merge with alejandra's two versions (explicit update rule).

@@

@@

  \begin{itemize}
  \item deploy models to different robotic systems: Nao, SimpleArm,
    Pointmass, two-wheeled
  \item timeseries analysis
  \item learning transient (arbitrarily fast, see Tin + Poon)
  \item explicitly map out the acquired models by sweeping the inputs and
    record their outputs
  \item what happens under perturbation?
  \item long-term adaptation effects: are we only plastic or are we also
    stable? do new adaptations overwrite previous ones? does a given
    approximator become saturated (just think how critical weight
    initialization in neural networks can be) in terms of its adaption
    capacity?, can be enforced via decay schedules of learning rate
    etc
  \end{itemize}

@@

Discuss, compare with existing approaches like std fwd/inv model
  pairs or reinforcement learning
